% !TEX root = ../../debate_casefile.tex

\section{Reporting from the Middle East}

Reporers are our ees and ears in the world.

Foreign reporters don't cover one topic, like just politics or just economics. They shift from topic to topic tackling the most erelevant topics

At the begening, the correspondents were the ambassadors, whod bring the foreing lands, gossip.

As the profession of a correspondant became stablished, the possition woild be filled in by elite (straight, white, middle aged men) people and located in elite cities (new york, berlin, etc).

Africa, latin america or SEA are few, while EU, USA have far many, which \textbf{narrows our perception of the worlds}. Foreign correstpondants are expensive to maintain from the point of view of a 

\subsection{Foreign-Foreing Corre}
Nationals who are payed to report to a company

\subsection{Parachute correspondants} 
Deployed in some time

\subsection{Free lance correspondants}
A good way to research, but the exclusivity is reduced.


We need experts to find what regimes do.

The middle east, Israel and Palestine is one of the most complicated regions to cover. 

\subsection{Tel aviv}

Tel aviv is expensive, and nice place to live in. Cost of living there is in the orders of california, and when youre there you dont feel that conflict is going on.


Israel is comprised of:
\begin{itemize}
	\item 8 million people
	\item 75\% jews
	\item 20\% muslim (who have israel passports and speak hebrew). They usually have issues with palestinian family members.
\end{itemize}

In Gaza
\begin{itemize}
	\item 2 million
	\item 99.7\% muslim
	\item Blockaded by walls and marine stops. Only few can move freely (medical emergencies or rich people)
	\item Very densly populated. \textbf{Same order of Hong Kong}, but with far less resources and destroyed.
\end{itemize}


On the west bank:
\begin{itemize}
	\item 3 million
	\item Walled up
	\item 85\% muslim
	\item 15\% Jew 
\end{itemize}



\subsection{Gaza strip}

Living is complicated:
\begin{itemize}
	\item Destroyed
	\item No energy security
	\item No
\end{itemize}

Very young
\begin{itemize}
	\item Average age is 21 years old
	\item In the 80s had a large population boom (4 kids per family)
	\item High unemployment, 50\%  in an underperforming economy.
	\item Social pressure: men need jobs to be fulfilled.
\end{itemize}


\subsubsection{Migration}
Young people without perspective have nothing to loose.
People would fill the streets with nothing to loose.

\subsubsection{Fatah}
A political party that lost control of Gaza to Hamas.

The EU and US pay the samalry to former members of political parties after they were fired.

This was done with hte purpose of keeping them in social stability.


\subsubsection{Hamas} 
The currently controlling political party. It's a Palestinian Sunni-Islamic fundamentalist organization. It also governs Gaza independently of the Palestinian Authority.

\begin{itemize} \index{Sex!Repression!Gaza}
	\item Women are opressed, headscarf, no sex before marriage, forced companions.
	\item People are expected to have sex after marriage.
	\item If you don't have a job, you cant get married.
	\item Huge sexual repression
\end{itemize}

\paragraph{Who is Hamas}

It's a politcal party in powr. An organization that does charity work and help society. 
Israel calls them terrorists, but from the Gazan perespective, they do more good than bad.

The western news coverage hardly covered the layers from the perspective of Hamas.



\subsubsection{Egypt and Gaza}

Theres networks of underground tunnels that connect these regions. 

People and cars can fit inside.

This border became a complicated region. Theyd create weapons and smuggling tunnels.

During the war, both Egypt and Israel wanted this area stopped, as it would also provide weaons to other muslim extremist groups. Egypt closed its borders and flooded the tunnels.

The \textbf{contribution of Egypt} in this war is often overlooked.



\section{The war}

On a simple sequence:
\begin{enumerate}
	\item On june 12 2014, a murder of a couple of jewish kids in the West bank. Israel army blamed Hamas.
	\item Some jewish kids took a kid from palestine, and burned him as a form of \textbf{revenge killing}.
	\item This lead to arrests and demonstrations on both sides.
	\item Then, israelis and palestinians started bombarding eachother.
	\item Small attacks through tunnels from palestinans would be done to Israel.
\end{enumerate}

This whole escalation happened in a matter of days.

The Israely population wanted the war to end quickly. With their superior military power they invaded.


\subsubsection{The green zone} \index{Journalism!War journalism}

Its a section that was agreed to be peaceful.

This is where journalist live, as both Hamas and Israel know that is convienient to both countries to have journalists engaged in the confilict.

Freelance journalists in war torn areas get payed absurdly large sums of money for covering the war. This could induce a \textbf{conflict of interest}, a lack of empathy to the pain of the people, doing no throguh investigation on the context of the events.

It's hard for journalists to stay unbiasad in this conflict when communication departmens from Israel are far more prepared and can easily bias the information that journalists recieve. Hamas, don't have these resources, so there's no correction. It requires very prepared foreign correspondents that speak all languages, and are ready to get out of the protected cliques of Israel.


\subsubsection{What has changed} 

Nothing. The war officially lasted 2 months, but ther has been no change since then.

The state of the people are still delicate. 
\begin{enumerate}
	\item Palestinians are still frustrated with their limited future.
	\item Trump wants US embassy in Jerusalem.
\end{enumerate}

A \textbf{similar conflict} such as the one that started could be on the horizon.

