% !TEX root = debate_casefile.tex


\section*{Clashing}

A clash is a \textbf{question which has to be answered} by both sides of the bench. Depending on the motion, their relevance becomes more valuable. The same question will have different answers from either bench. The debate revolves around finding the \textbf{key differences} between both sides (eg. status quo vs proposed change).

\begin{itemize}
	\item Believe
	\begin{itemize}
		\item Whether $x$ is \textbf{true}.
		\item Whether $x$ is \textbf{justified}.
		\item Whether $x$ has a \textbf{significant impact}, positive or negative.
	\end{itemize}
	\item Regret (expect counter-prop)
	\begin{itemize}
		\item Whether the existing \textbf{harm} is/has/will be there, locally or globally.
		\item If there are \textbf{self-correcting} mechanisms.
		\item The consequences on \textbf{the act} of regretting (ie. the message it might send).
	\end{itemize}
	\item Would (expect policy model)
	\begin{itemize}
		\item Whether $x$ is \textbf{urgent} or necessary.
		\item Whether $x$ is \textbf{justified}.
		\item Whether $x$ is \textbf{effective} at solving the problem.
		\item If there are \textbf{side-benefits} (ie. the subtle consequences).
	\end{itemize}
	\item Supports (expect counter-prop)
	\begin{itemize}
		\item Whether $x$ is \textbf{solving} the problem intuitively.
		\item Whether $x$ is \textbf{necessary}.
		\item Whether $x$ has \textbf{exclusive} large benefits.
		\item Whether $x$ is in line with the \textbf{value(s)} of the \textit{actor} supporting it.
		\begin{itemize}
			\item With \textit{actors}, it should be proved that \textbf{their involvement} is necessary.
		\end{itemize}
	\end{itemize}
	\item Preferred to
	\begin{itemize}
		\item Whether $x$ or $y$ provide a \textbf{better solution} to the common problem.
		\begin{itemize}
			 \item Is either: (more) self-sustainable, faster, has a larger group to impact, more cost efficient, or \textit{principally} more correct than the other.
		 \end{itemize} 
		 \item Whether $x$ or $y$ give more benefit than the other in the \textbf{short/long term}.
	\end{itemize}
	\item Bring more harm than good
	\begin{itemize}
		\item Whether the \textbf{nature} of $x$ gives more substantial harm than good.
		\begin{itemize}
			\item Whether the harm/good is \textbf{replaceable}.
			\item A weigh-off between \textbf{size vs quality} of the impact (ie. war casualties: civilians vs soldiers)
		\end{itemize}
		\item Whether the nature of $x$ gives more \textbf{likelihood} to harm than good.
		\item Whether the nature of $x$ gives more \textbf{relevance} to harm than good (note that both sides will have to do such comparison on their own terms.)
	\end{itemize}
\end{itemize}

\vfill
\pagebreak