% !TEX root = ../debate_casefile.tex

\section{Drugs} \index{Drugs}

	\subsection{War on drugs} \index{Drugs!War on drugs}

	Its latest iteration can be traced to \textbf{George W. Bush}.


	\subsubsection{Consequences}


\subsection{Homeopathy} \index{Drugs!Homeopathy} 

	``Faith can move mountains, but sugar water can't cure cancer'', \citet{homeopathy_kurzgesagt}.

	It's the most popular alternative medecine. It's working principle is the following:
	\begin{itemize}
		\item `like cures like', remedies for fever use sources of fever.
		\item `potentializer'. Ingredientes dilute the concentration of the ailment soruce (orders of 1:10$^{20}$)
		\item The concentration is so low it's often stated that the \textbf{escence} of the ailment is still within the homeopatic medicine.
	\end{itemize}


	Doing no harm was better than actually harming, which is why it became the most popular alternative medicine

	Modern medicine has performed enough tests and reviews to proove that homeopathy statistically doesn't directly provide any cure for diseases. All it provides is \textbf{placebo}.

	\subsubsection{Who cares why it works} \index{Drugs!Placebo}

		Theres personal evidence going around of people who felt better after placebo treatments. \textbf{Trust} and \textbf{time} have enough of an influence on how people feel
		\begin{itemize}
			\item Animals and kids react to the trust their guardians have on the cure
			\item Human bodies cure their own diseases. Medicnce treatments strengthen their systems enough so that their cured faster.
		\end{itemize}

	\subsubsection{Homeopathy as big pharma} \index{Drugs!Big pharma!Homeopathy}
		\begin{itemize}
			\item they have absurd profit margins
			\item they have lobbying power
			\item \$17B expected industry for 2030
		\end{itemize}


	\subsubsection{Side effects}
		Trusting in homeopathy multiplies the perception that traditional medicine aren't effective. (Antivaxxers) \index{Drugs!Antivaxxers}

		This makes people doubt wether to get the treatment for themselves (or \textbf{their children})


	\subsubsection{Modern medicine vs Homeopathy} \index{Drugs!Modern medicine}

		Modern medicine is overcrowded and impersonal. Patients moving from doctor to specialist feeling scared for their lives or invisible.

		Modern medicine can learn from the personal treatment that homeopathy have on their patients, which talk personally about the lives of their patients.


\subsection{Big pharma} \index{Big pharma}

	Wall Street wants growth but that's hard to do in a business \textbf{where the number of patients for most ailments don't increase.

	If the costs of medicine aren't kept high, the companies will go **in debt** which leads to:
	\begin{itemize}
		\item loss of jobs
		\item loss of knowledge
		\item temporary **loss of production** of medicine which could cause death if patients.
		\subitem most likely to the less profitable drugs. (Which could have no alternative formula)
	\end{itemize}


	\subsubsection{Valeant}

		The latest company which used capital investments to increase profits, while cutting costs for R&D (from 20\% of income to 3\%).

		Their model rellied on increasing income by increasing the cost of medicine, as the number of sick people doesn't change

		All of these practices were legal and rellied on investors to prefer short term profit

		The former CEO was recently convicted for invester fraud, which means that in the current justice system this practice of arbitrarily raising the price of medicine is immoral, but \textbf{perfectly legal}. Part of the reason why the trail got so delayed was by the inability to have \textbf{neutral jury} that would have no personal opinion to the accusee.



