% !TEX root = ../debate_casefile.tex

\section{Human trafficking} 

Defined as the inducing a person by force, fraud, or coercion to perform acts of involuntary servitude, sex work, debt bondage, or slavery.

\subsection{How people are trapped}

	Example for sex workers:
	\begin{enumerate}
		\item Young women are tricked into relationships (by either men or women).
		\item They get them drugged, and force them into sex acts from which they can get blackmailed.
		\item This blackmail is used to push them into more sex acts.
		\item In some cases they get shipped into other parts of their country.
	\end{enumerate}

	Example for slave labor:
	\begin{itemize}
		\item A young person, often poor gets a lucrative job offer.
		\item Once they're working, they get drugged/kidnapped
		\item They get placed into fishing boats (east asia) or constructions (qatar) with no ability to escape (no passport / identification)
		\item They're forced to work under terrible conditions, few food, and little to no pay.
	\end{itemize}

	Example with corrupt police forces: \index{Corruption!Human trafficking}
	\begin{itemize}
		\item A poor person gets put into jail (local law enforcement)
		\item Before their documented into the system, they're offered to the local human traffickers for a bid
	\end{itemize}


\subsection{Economies of traffic} \index{Machine learning!Human trafficking}
	
	Usually, it's the job of people to follow the networks of money. Trailing behind:
	\begin{itemize}
		\item Sequential deposits in short periods of time
		\item Shipping services which are underloaded or overpayed
		\item Purchasing of expensive jewlery which acts as a form launder
	\end{itemize}

	With \textbf{machine learning}, banks and NGOs can discover this patterns much easier.

	If law enforcement and banks become more prepared, this only pushes criminals into acquiring better technology. \textbf{Cryptocurrencies} are a way for black market to move large sums of money without the need for the involvement of formal banks. \index{Cryptocurrencies!Human trafficking}






\subsection{Data} \index{Data!Human Trafficking}

	By gender, 75\% are women, and 25\% are men.

	Money involved:
	\begin{itemize}
		\item It's a 150 billion USD industry. (for reference, Apple 2017 made 50 bn in profits)
		\item  66\% to sex workers
		\item  33\% to forced labor
	\end{itemize}

	Number of people:
	\begin{itemize}
		\item Forced labor (16 million)
		\item Sexual workers (5 million)
	\end{itemize}

	Forced labor:
	\begin{itemize}
		\item Construction, mining or manufacturing (50\%)
		\item Domestic work (25\%)
		\item Agriculture (11\%)
	\end{itemize}





